Carbonate chemistry at Ny-Ålesund

### 2023-01-12 awipev-CO2.Rmd
refine time series + boxplot

# identify extremes
d_bp <- d_bp %>%
  dplyr::mutate(
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
  )
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="", y = "Salinity", x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = "Temperature (°C)", x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
  Mytheme(size_labs = size_labs)+
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = TeX("$pH_T$"), x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g2 + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
ggsave(filename = "figures/ts_boxplots.png", plot = g2)
```

>>>>

# identify extremes
d_bp <- d_bp %>%
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="", y = "Salinity", x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = "Temperature (°C)", x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
  Mytheme(size_labs = size_labs)+
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = TeX("$pH_T$"), x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=NULL, y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g2 + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
ggsave(filename = "figures/ts_boxplots.png", plot = g2)
